\documentclass[a4paper,10pt]{scrartcl} % KOMA-Script article
% Use letter when sending to US/other letter-based country
%\documentclass[letterpaper,10pt]{scrartcl}

\usepackage{joycv}

\begin{document}
\thispagestyle{empty}
\begin{cv}{\Author{António Alegria}}

  \Sep
  
  \PlaceAndDateOfBirth{Born in Lisbon, Portugal}{February 6, 1985}

  \Contact{email}{\href{mailto:antonio.mc.alegria@gmail.com}{antonio.mc.alegria@gmail.com}}

  \Contact{phone}{(+351) 965 558 738}

  \Contact{web}{\href{http://antonioalegria.com}{antonioalegria.com}}


  \Section{Profile}
  
  \Profile{I am a Software Engineer who loves designing and building systems that make sense of data, turning them into actionable insights for people and businesses in real-time and at scale. I am thrilled about solving challenging problems in elegant and efficient ways through the use of state-of-the art tools and by having an eye for quality.}


  \Section{Work Experience}

  \NewWorkExperience{Feb 2012--Ongoing}{FeedZai,}{Lisbon}

  \Description{Senior Software Engineer}{Currently the tech lead coordinating implementation of international Fraud Detection pilots and of SaaS Fraud API. I have been working as a Data Scientist and a lead Engineer in building core technology used in real-time Big Data, Predictive Analytics and Fraud Detection.}
  
  \Highlights{Highlights:} {
  \begin{itemize}[nosep,noitemsep,leftmargin=3.85em]
    \item Lead and co-developed the core data-processing and machine learning components for real-time fraud detection product. \Tech{Scala, Java, Akka, Hadoop, Twitter Storm, CEP, R}.
	  \item Co-designed and implemented Predictive Analytics module for continuous, real-time time-series forecasting. \Tech{Java, CEP, HTML5, Javascript}.
	  \item Responsible for certifying FeedZai Pulse with Cloudera CDH and integrating with SAP HANA, spearheading the partnership with SAP, which resulted in SAP Ventures' investment in FeedZai. \Tech{Java, Flume, SQL, SAP HANA}.
  \end{itemize}
  }
  
  \Sep


  \NewWorkExperience{Jul 2010--Feb 2012}{Portugal Telecom - SAPO.pt,}{Lisbon}

  \Description{Software Engineer}{Worked in the Big Data team developing event processing systems and in the Mobile Apps team as an Android developer.}

  \Highlights{Highlights (Big Data):} {
  \begin{itemize}[nosep,noitemsep,leftmargin=3.85em]
    \item Designed and implemented a real-time, automatic metric aggregator for in-house KPI management system. \Tech{Java, Esper, JSON, MQ}.
    \item Maintained SAPO Alerts - a domain-independent, real-time event subscription and filtering platform used by PT and 3\textsuperscript{rd} parties. \Tech{Java, XML, PostgreSQL, Netty, SOAP}.
  \end{itemize}
  }

  \Highlights{Highlights (Mobile):} {
  \begin{itemize}[nosep,noitemsep,leftmargin=3.85em]
    \item Implemented and shipped over 5 Android Apps including SAPO News -- SAPO's flagship App with over 100,000 users. \Tech{Android, Java, SQLite, HTML5, Javascript}.
    \item Spearheaded Scrum adoption.
    \item Proactively managed and coordinated a large part of the SAPO News mobile Apps project.
  \end{itemize}
  }

  \Sep


  \NewWorkExperience{Sep 2008--Jul 2010}{Portugal Telecom,}{Lisbon}

  \Description{Software Engineer}{Core developer of real-time analytics and Business Activity Monitoring system - Pulso - using Complex Event Processing (CEP).}

  \Highlights{Highlights:} {
  \begin{itemize}[nosep,noitemsep,leftmargin=3.85em]
    \item Designed and implemented core CEP system in Pulso. \Tech{Esper, JRuby, Java, ActiveMQ, Starling, MySQL}.
    \item Designed and implemented domain-independent BAM patterns and rules for business process and application monitoring solutions. \Tech{Esper}.
    \item Implemented tens of real monitoring scenarios for several mission-critical business processes and applications in PT. \Tech{Esper, Ruby}.
  \end{itemize}
  }

  \Sep


  \NewWorkExperience{Nov 2007--Aug 2008}{Portugal Telecom,}{Lisbon}

  \Description{Software Engineer Intern}{Developed and applied MSc research. Results were tested in three real-word Information Systems Architectures. Helped development of in-house automatic network application and infrastructure discovery system.}
  
  \Highlights{Highlights:} {
  \begin{itemize}[nosep,noitemsep,leftmargin=3.85em]
    \item Designed, implemented and applied an automatic IT architecture verification and discovery system that uses deep passive traffic analysis and rule-based logic inference to run a ``fact-check'' on a proposed IT architecture model. \Tech{Logtalk/Prolog, Ruby, C and an assortment of network traffic analysis tools}.
    \item Designed and implemented a wide range of deep packet analysis probes for enterprise application identification and error detection. \Tech{C, Ruby, PADS}.
  \end{itemize}
  }

  \Sep

  \NewWorkExperience{Feb 2005--Jun 2006}{\small{INESC-ID - Distributed Systems Group},}{Lisbon}

  \Description{Intern}{Researched and implemented ad-hoc (mesh) network applications for mobile devices using Bluetooth, RF-ID and Microsoft .Net Compact Framework.}



  \Section{Higher Education}

  \NewWorkExperience{Nov 2009}{Instituto Superior Técnico,}{Lisbon}

  \Description{MSc in Computer Engineering}{Major: Software Engineering\ \ $\cdotp$\ \ Minor: Distributed Systems\newline Thesis: ``Automatic Verification of IT Architecture Models for Networked Information Systems''\newline Thesis Grade: 19/20\ \ $\cdotp$\ \  GPA: 17/20}

  \Sep


  \NewWorkExperience{Jul 2007}{Instituto Superior Técnico,}{Lisbon}

  \Description{BSc in Computer Engineering}{Major: Software Engineering\ \ $\cdotp$\ \ Minor: Distributed Systems\ \ $\cdotp$\ \  GPA: 16/20}



  \Section{Training and Certification}

  \NewTraining{Sep 2012}{IELTS General Exam}

  \SimpleDescription{IELTS Band Score: 8.5/9}

  \TrainingSep

  \NewTraining{Jul 2011}{Lisbon Machine Learning School}

  \SimpleDescription{Google-sponsored international summer school.}

  \TrainingSep

  \NewTraining{Jan 2011}{Scrum Alliance -- Certificate Scrum Master}
  
  \SimpleDescription{Institution: \spacedlowsmallcaps{Vantagem+}}

  \TrainingSep

  \NewTraining{Oct 2009}{Initial Pedagogical Training for Trainers}

  \SimpleDescription{Institution: \spacedlowsmallcaps{Portugal Telecom Inovação, SA}}

  \TrainingSep

  \NewTraining{Jun 2002}{Certificate of Proficiency in English}

  \SimpleDescription{Institution: \spacedlowsmallcaps{University of Cambdrige, Local Examinations Syndicate}}

  \Section{Publications}

  \Publication{\textbf{ALEGRIA, A.}, AND VASCONCELOS, A. \textbf{2010}. IT Architecture Automatic Verification: A Network Evidence-based Approach. In \textit{Proceedings of the Fourth IEEE International Conference on Research Challenges in Information Science}, RCIS 2010, Nice, France, May 2010, LOUCOPOULOS, P. AND CAVARERO, J.L., Eds. 1-12, \href{http://j.mp/rcis2010paper}{http://j.mp/rcis2010paper}.}


  \newpage

  \Section{Conferences \& Events}

  \NewConference{Sep 2012}{SAP HANA Bootcamp,}{Dublin, Ireland}

  \TrainingSep

  \NewConference{Nov 2012}{Codebits VI,}{Lisbon}
  
  \Description{Awarded Team}{Built a distributed slide presentation platform with support for real-time metrics and crowdsensing from mobile device sensors. Our team placed 4th in 100. \Tech{Node.js, HTML5, Javascript, CSS}.}
  
  \TrainingSep

  \NewConference{Nov 2011}{Codebits V,}{Lisbon}

  \Description{Speaker}{Presented talk \textit{Complex Event Processing with Esper}.\newline Video: \href{http://j.mp/cepvideo2011}{http://j.mp/cepvideo2011}\ \ $\cdotp$\ \  Slides: \href{http://j.mp/cepslides2011}{http://j.mp/cepslides2011}}
  
  \TrainingSep

  \NewConference{May 2011}{Startup Weekend,}{Coimbra}

  \TrainingSep

  \NewConference{May 2010}{RCIS 2010,}{Nice, France}
  
  \Description{Speaker}{Presented paper \textit{IT Architecture Automatic Verification: A Network Evidence-based Approach}.\newline Slides: \href{http://j.mp/rcis2010slides}{http://j.mp/rcis2010slides}}

  \Section{Main Skills \& Interests}

  \Description{Prog. Languages}{Java\ \ $\cdotp$\ \ Scala\ \ $\cdotp$\ \ (J)Ruby\ \ $\cdotp$\ \ R\ \ $\cdotp$\ \ Other: Javascript, C, Prolog/Logtalk}

  \TrainingSep

  \Description{Dist. Computing}{Hadoop\ \ $\cdotp$\ \ Twitter Storm\ \ $\cdotp$\ \ Akka\ \ $\cdotp$\ \ Scalding\ \ $\cdotp$\ \ Pig}

  \TrainingSep
  
  \Description{Messaging}{ActiveMQ\ \ $\cdotp$\ \ Starling/Kestrel\ \ $\cdotp$\ \ SAPO Broker\ \ $\cdotp$\ \ Flume}

  \TrainingSep

  \Description{Databases}{PostgreSQL\ \ $\cdotp$\ \ MySQL\ \ $\cdotp$\ \ Cassandra\ \ $\cdotp$\ \ SAP HANA\ \ $\cdotp$\ \ MongoDB}

  \TrainingSep
  
  \Description{Other Platforms}{Esper\ \ $\cdotp$\ \ Weka\ \ $\cdotp$\ \ Sinatra\ \ $\cdotp$\ \ Node.js}

  \Sep
  
  \SimpleDescription{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \  \ Fluent}
  
  \vspace{0.5em}
  
  \SimpleDescription{\parbox{\langbox}{\textsc{Spanish}}\ \ $\cdotp$\ \  \ Competent Listening and Speaking}

  \vspace{0.5em}
  
  \SimpleDescription{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \  \ Competent Listening and Limited Speaking}
  \MarginDate{Languages}

  \vspace{0.5em}

  % \SimpleDescription{\parbox{\langbox}{\textsc{Japanese}}\ \ $\cdotp$\ \  \ Elementary}
  % 
  % \vspace{0.5em}
  
  \SimpleDescription{\parbox{\langbox}{\textsc{Portuguese}}\ \ $\cdotp$\ \  \ Native}
  
  \Sep

  \Description{Interests}{Data Science\ \ $\cdotp$\ \ Big Data\ \ $\cdotp$\ \ Agile Development\ \ $\cdotp$\ \ Product Design\ \ $\cdotp$\ \ Project Management\ \ $\cdotp$\ \ Predictive Analytics\ \ $\cdotp$\ \ Fraud Detection}
  
  \Sep

\enlargethispage{\baselineskip}
\end{cv}
\end{document}

